Verifying Demonstrations

### 2018-08-21 paper/adversary-model.tex
Tries to name the different models
Updates names of adversary models

\paragraph{The base protester-privacy model}

@@

\paragraph{A stronger adversary}

Now we define an adversary \(A^W\), where the witness \(W\) learns the 
protester \(P\)'s identity.
(\(P\) will also learn \(W\)'s identity.)
However, \(S\) still does not learn \(P\)'s identity.

We also define an adversary \(A^{W,S}\), where \(S\) also learns \(P\)'s 
identity.

>>>>

\paragraph{The base malicious witness--storage model}

@@

\paragraph{The stronger malicious witness--storage model}

Now the witness \(W\) learns the protester \(P\)'s identity.
(\(P\) will also learn \(W\)'s identity.)
However, \(S\) still does not learn \(P\)'s identity.

\paragraph{The strongest malicious witness--storage model}

Now \(S\) also learns \(P\)'s identity.
